---
title: "Projectttt"
author: "Pandarinath"
date: "2023-12-09"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```


```{r}
library(readxl)
Data_Train <- read_excel("C:/Users/HP/Downloads/Data_Train.xlsx")
View(Data_Train)
```


```{r}

str(Data_Train)

```


##Total number of airlines


```{r}

# Get the frequency table for a categorical variable (replace "Airline" with your actual column name)
table(Data_Train$Airline)
```



##Descriptive statistics on the dataset

```{r}
summary(Data_Train)

```

```{r}
mean_price <- mean(Data_Train$Price)
median_price <- median(Data_Train$Price)
sd_price <- sd(Data_Train$Price)
print(paste("The mean of flight price is",mean_price))

print(paste("The Standard deviation of flight price is",sd_price))

print(paste("The median of flight price is",median_price))

t_test_result = t.test(Data_Train$Price, conf.level = 0.95)
t_test_result

```
Importing datasets with same airlines
```{r}
library(readxl)
output_tables_airasia <- read_excel("C:/Users/HP/Downloads/output_tables.xlsx", 
    sheet = "Air Asia")
View(output_tables_airasia)
```

```{r}
library(readxl)
output_tables_airindia <- read_excel("C:/Users/HP/Downloads/output_tables.xlsx", 
    sheet = "Air India")
View(output_tables_airindia)

```

```{r}
library(readxl)
output_tables_goair <- read_excel("C:/Users/HP/Downloads/output_tables.xlsx", 
    sheet = "GoAir")
View(output_tables_goair)

```

```{r}
library(readxl)
output_tables_indigo <- read_excel("C:/Users/HP/Downloads/output_tables.xlsx", 
    sheet = "IndiGo")
View(output_tables_indigo)
```

```{r}
library(readxl)
output_tables_jetairways <- read_excel("C:/Users/HP/Downloads/output_tables.xlsx", 
    sheet = "Jet Airways")
View(output_tables_jetairways)

```

```{r}
library(readxl)
output_tables_jetairwaysbusiness <- read_excel("C:/Users/HP/Downloads/output_tables.xlsx", 
    sheet = "Jet Airways Business")
View(output_tables_jetairwaysbusiness)

```

```{r}
library(readxl)
output_tables_multipleairways <- read_excel("C:/Users/HP/Downloads/output_tables.xlsx", 
    sheet = "Multiple carriers")
View(output_tables_multipleairways)

```

```{r}

library(readxl)
output_tables_multiplecarriers_premium <- read_excel("C:/Users/HP/Downloads/output_tables.xlsx", 
    sheet = "Multiple carriers Premium econo")
View(output_tables_multiplecarriers_premium)

```

```{r}
library(readxl)
output_tables_spicejet <- read_excel("C:/Users/HP/Downloads/output_tables.xlsx", 
    sheet = "SpiceJet")
View(output_tables_spicejet)
```

```{r}
library(readxl)
output_tables_vistara <- read_excel("C:/Users/HP/Downloads/output_tables.xlsx", 
    sheet = "Vistara")
View(output_tables_vistara)

```



##Mean,Median,Standard Deviation of Air asia Flight Prices
```{r}
mean_price_airasia = mean(output_tables_airasia$Price)
median_price_airasia = median(output_tables_airasia$Price)
sd_price_airasia = sd(output_tables_airasia$Price)

print(paste("The mean of flight price is",mean_price_airasia))

print(paste("The Standard deviation of flight price is",sd_price_airasia))

print(paste("The median of flight price is",median_price_airasia))

hist(output_tables_airasia$Price, main = "Flight Price Distribution", xlab = "Price")

# Create a boxplot for the 'price' variable
boxplot(output_tables_airasia$Price, main = "Flight Price Boxplot", ylab = "Price")

t_test_airasia = t.test(output_tables_airasia$Price, conf.level = 0.95)
t_test_airasia



```
##Mean,median,standard deviation of air india flight prices

```{r}
mean_price_airindia = mean(output_tables_airindia$Price)
median_price_airindia = median(output_tables_airindia$Price)
sd_price_airindia = sd(output_tables_airindia$Price)

print(paste("The mean of flight price is",mean_price_airindia))

print(paste("The Standard deviation of flight price is",sd_price_airindia))

print(paste("The median of flight price is",median_price_airindia))

hist(output_tables_airindia$Price, main = "Flight Price Distribution", xlab = "Price")

# Create a boxplot for the 'price' variable
boxplot(output_tables_airindia$Price, main = "Flight Price Boxplot", ylab = "Price")

t_test_airindia = t.test(output_tables_airindia$Price, conf.level = 0.95)
t_test_airindia
```


```{r}
mean_price_goair = mean(output_tables_goair$Price)
median_price_goair = median(output_tables_goair$Price)
sd_price_goair = sd(output_tables_goair$Price)

print(paste("The mean of flight price is",mean_price_goair))

print(paste("The Standard deviation of flight price is",sd_price_goair))

print(paste("The median of flight price is",median_price_goair))
hist(output_tables_goair$Price, main = "Flight Price Distribution", xlab = "Price")

# Create a boxplot for the 'price' variable
boxplot(output_tables_goair$Price, main = "Flight Price Boxplot", ylab = "Price")

t_test_goair = t.test(output_tables_goair$Price, conf.level = 0.95)
t_test_goair

```

```{r}
mean_price_indigo = mean(output_tables_indigo$Price)
median_price_indigo = median(output_tables_indigo$Price)
sd_price_indigo = sd(output_tables_indigo$Price)

print(paste("The mean of flight price is",mean_price_indigo))

print(paste("The Standard deviation of flight price is",sd_price_indigo))

print(paste("The median of flight price is",median_price_indigo))

hist(output_tables_indigo$Price, main = "Flight Price Distribution", xlab = "Price")

# Create a boxplot for the 'price' variable
boxplot(output_tables_indigo$Price, main = "Flight Price Boxplot", ylab = "Price")

t_test_indigo = t.test(output_tables_indigo$Price, conf.level = 0.95)
t_test_indigo
```


```{r}
mean_price_jetairways = mean(output_tables_jetairways$Price)
median_price_jetairways = median(output_tables_jetairways$Price)
sd_price_jetairways = sd(output_tables_jetairways$Price)

print(paste("The mean of flight price is",mean_price_jetairways))

print(paste("The Standard deviation of flight price is",sd_price_jetairways))

print(paste("The median of flight price is",median_price_jetairways))

hist(output_tables_indigo$Price, main = "Flight Price Distribution", xlab = "Price")

# Create a boxplot for the 'price' variable
boxplot(output_tables_indigo$Price, main = "Flight Price Boxplot", ylab = "Price")

t_test_jetairways = t.test(output_tables_jetairways$Price, conf.level = 0.95)
t_test_jetairways

```

```{r}
mean_price_jetbusiness = mean(output_tables_jetairwaysbusiness$Price)
median_price_jetbusiness = median(output_tables_jetairwaysbusiness$Price)
sd_price_jetbusiness = sd(output_tables_jetairwaysbusiness$Price)

print(paste("The mean of flight price is",mean_price_jetbusiness))

print(paste("The Standard deviation of flight price is",sd_price_jetbusiness))

print(paste("The median of flight price is",median_price_jetbusiness))

hist(output_tables_jetairwaysbusiness$Price, main = "Flight Price Distribution", xlab = "Price")

# Create a boxplot for the 'price' variable
boxplot(output_tables_jetairwaysbusiness$Price, main = "Flight Price Boxplot", ylab = "Price")

t_test_jetairwaysbusiness = t.test(Data_Train$Price, conf.level = 0.95)
t_test_jetairwaysbusiness
```

```{r}
mean_price_multiplecarriers = mean(output_tables_multipleairways$Price)
median_price_multipecarriers = median(output_tables_multipleairways$Price)
sd_price_multiplecarriers = sd(output_tables_multipleairways$Price)

print(paste("The mean of flight price is",mean_price_multiplecarriers))

print(paste("The Standard deviation of flight price is",sd_price_multiplecarriers))

print(paste("The median of flight price is",median_price_multipecarriers))

hist(output_tables_multipleairways$Price, main = "Flight Price Distribution", xlab = "Price")

# Create a boxplot for the 'price' variable
boxplot(output_tables_multipleairways$Price, main = "Flight Price Boxplot", ylab = "Price")

t_test_multiplecarriers = t.test(output_tables_multipleairways$Price, conf.level = 0.95)
t_test_multiplecarriers
```

```{r}
mean_price_mulprem = mean(output_tables_multiplecarriers_premium$Price)
median_price_mulprem = median(output_tables_multiplecarriers_premium$Price)
sd_price_mulprem = sd(output_tables_multiplecarriers_premium$Price)

print(paste("The mean of flight price is",mean_price_mulprem))

print(paste("The Standard deviation of flight price is",sd_price_mulprem))

print(paste("The median of flight price is",median_price_mulprem))

hist(output_tables_multiplecarriers_premium$Price, main = "Flight Price Distribution", xlab = "Price")

# Create a boxplot for the 'price' variable
boxplot(output_tables_multiplecarriers_premium$Price, main = "Flight Price Boxplot", ylab = "Price")

t_test_mulprem = t.test(output_tables_multiplecarriers_premium$Price, conf.level = 0.95)
t_test_mulprem
```


```{r}
mean_price_spicejet = mean(output_tables_spicejet$Price)
median_price_spicejet = median(output_tables_spicejet$Price)
sd_price_spicejet = sd(output_tables_spicejet$Price)

print(paste("The mean of flight price is",mean_price_spicejet))

print(paste("The Standard deviation of flight price is",sd_price_spicejet))

print(paste("The median of flight price is",median_price_spicejet))

hist(output_tables_spicejet$Price, main = "Flight Price Distribution", xlab = "Price")

# Create a boxplot for the 'price' variable
boxplot(output_tables_spicejet$Price, main = "Flight Price Boxplot", ylab = "Price")

t_test_spicejet = t.test(output_tables_spicejet$Price, conf.level = 0.95)
t_test_spicejet
```

```{r}
mean_price_vistara = mean(output_tables_vistara$Price)
median_price_vistara = median(output_tables_vistara$Price)
sd_price_vistara = sd(output_tables_vistara$Price)

print(paste("The mean of flight price is",mean_price_vistara))

print(paste("The Standard deviation of flight price is",sd_price_vistara))

print(paste("The median of flight price is",median_price_vistara))

hist(output_tables_vistara$Price, main = "Flight Price Distribution", xlab = "Price")

# Create a boxplot for the 'price' variable
boxplot(output_tables_vistara$Price, main = "Flight Price Boxplot", ylab = "Price")

t_test_vistara = t.test(output_tables_vistara$Price, conf.level = 0.95)
t_test_vistara

```



```{r}
# Assuming your data frame is named Data_Train
Data_Train$Duration <- as.character(Data_Train$Duration)

# Extract hours and minutes
hours <- as.numeric(substring(Data_Train$Duration, 1, regexpr("h", Data_Train$Duration) - 1))
minutes <- as.numeric(substring(Data_Train$Duration, regexpr(" ", Data_Train$Duration) + 1, nchar(Data_Train$Duration) - 1))

# Calculate total duration in minutes
total_minutes <- hours * 60 + minutes

# Replace the original 'Duration' column with the new numeric column
Data_Train$Duration <- total_minutes


```


```{r}
sum(is.na(Data_Train$Price))
sum(is.na(Data_Train$Duration))

```

```{r}
Data_Train <- na.omit(Data_Train)

```


```{r}

cov(Data_Train$Price, Data_Train$Duration)
```

```{r}
cor(Data_Train$Price, as.numeric(Data_Train$Duration), use = "complete.obs")

```


##Hypothesis testing 
null hypothesis: mean prices for short duration flights are equal to mean prices for long duration flights.
alternative hypothesis: mean prices for short duration flights are different from mean prices for long duration flights.
t
$H_0: \mu=9000$  
$H_a: \mu \neq 9000$ 
```{r}
# Example: Z-test with known population standard deviation
library(TeachingDemos)
result_allairlines = z.test(Data_Train$Price, mu = 9000, sd_price, alternative = "two.sided")


result_allairlines
```

```{r}
hist(Data_Train$Price, main = "Histogram of Flight Prices", xlab = "Price", col = "lightblue")
```
```{r}
install.packages("ggplot2")

```
```{r}
# Assuming you have the necessary libraries installed
library(ggplot2)

# Your hypothesis testing output
test_result <- list(
  mean = 9086.443,
  std_dev = 44.619,
  p_value = 0.0527,
  conf_interval = c(8998.991, 9173.895)
)

# Create a histogram
histogram <- ggplot(Data_Train, aes(x = Price)) +
  geom_histogram(binwidth = 500) +  # Adjust binwidth as needed
  labs(title = "Flight Price Distribution") +
  xlab("Price") +
  ylab("Frequency")

# Add mean and confidence interval
histogram <- histogram +
  geom_vline(xintercept = test_result$mean, color = "red", linetype = "dashed", size = 1) +
  geom_text(aes(x = test_result$mean, y = 0, label = "Mean"), vjust = -0.5, color = "red") +
  geom_errorbar(aes(x = (test_result$conf_interval[1] + test_result$conf_interval[2]) / 2,
                    ymin = -Inf, ymax = Inf),
                width = 500, color = "blue", size = 1, alpha = 0.5) +
  geom_rect(xmin = test_result$conf_interval[1], xmax = test_result$conf_interval[2],
            ymin = 0, ymax = Inf, fill = "gray", alpha = 0.3)

# Display the plot
print(histogram)

```



##Linear regression

##To check summary statistics
```{r}
summary(Data_Train)

```
##Predicting flight prices based on duration,total number of stops

```{r}
# Example: Convert Total_Stops to numeric
Data_Train$Total_Stops <- as.numeric(factor(Data_Train$Total_Stops, levels = c("non-stop", "1 stop", "2 stops", "3 stops", "4 stops")))

```

##Implementing the model
```{r}
# Example: Using lm() function for linear regression
model <- lm(Price ~ Duration + Total_Stops, data = Data_Train)
model

```
##Converting duration and totalstops to numeric in all airlines data

```{r}
# Assuming your data frame is named Data_Train
output_tables_airasia$Duration <- as.character(output_tables_airasia$Duration)

# Extract hours and minutes
hours <- as.numeric(substring(output_tables_airasia$Duration, 1, regexpr("h", output_tables_airasia$Duration) - 1))
minutes <- as.numeric(substring(output_tables_airasia$Duration, regexpr(" ", output_tables_airasia$Duration) + 1, nchar(output_tables_airasia$Duration) - 1))

# Calculate total duration in minutes
total_minutes <- hours * 60 + minutes

# Replace the original 'Duration' column with the new numeric column
output_tables_airasia$Duration <- total_minutes


output_tables_airasia <- na.omit(output_tables_airasia)




```


```{r}
# Example: Convert Total_Stops to numeric
output_tables_airasia$Total_Stops <- as.numeric(factor(output_tables_airasia$Total_Stops, levels = c("non-stop", "1 stop", "2 stops", "3 stops", "4 stops")))
```
##Implementing model for airasia
```{r}
# Example: Using lm() function for linear regression
model <- lm(Price ~ Duration + Total_Stops, data = output_tables_airasia)
model

```


```{r}
# Assuming your data frame is named Data_Train
output_tables_airindia$Duration <- as.character(output_tables_airindia$Duration)

# Extract hours and minutes
hours <- as.numeric(substring(output_tables_airindia$Duration, 1, regexpr("h", output_tables_airindia$Duration) - 1))
minutes <- as.numeric(substring(output_tables_airindia$Duration, regexpr(" ", output_tables_airindia$Duration) + 1, nchar(output_tables_airindia$Duration) - 1))

# Calculate total duration in minutes
total_minutes <- hours * 60 + minutes

# Replace the original 'Duration' column with the new numeric column
output_tables_airindia$Duration <- total_minutes


output_tables_airindia <- na.omit(output_tables_airindia)

```


```{r}
# Example: Convert Total_Stops to numeric
output_tables_airindia$Total_Stops <- as.numeric(factor(output_tables_airindia$Total_Stops, levels = c("non-stop", "1 stop", "2 stops", "3 stops", "4 stops")))
```

##Implementing model for airindia
```{r}
# Example: Using lm() function for linear regression
model <- lm(Price ~ Duration + Total_Stops, data = output_tables_airindia)
model
```
```{r}
# Assuming your data frame is named Data_Train
output_tables_goair$Duration <- as.character(output_tables_goair$Duration)

# Extract hours and minutes
hours <- as.numeric(substring(output_tables_goair$Duration, 1, regexpr("h", output_tables_goair$Duration) - 1))
minutes <- as.numeric(substring(output_tables_goair$Duration, regexpr(" ", output_tables_goair$Duration) + 1, nchar(output_tables_goair$Duration) - 1))

# Calculate total duration in minutes
total_minutes <- hours * 60 + minutes

# Replace the original 'Duration' column with the new numeric column
output_tables_goair$Duration <- total_minutes


output_tables_goair <- na.omit(output_tables_goair)


```

```{r}
# Example: Convert Total_Stops to numeric
output_tables_goair$Total_Stops <- as.numeric(factor(output_tables_goair$Total_Stops, levels = c("non-stop", "1 stop", "2 stops", "3 stops", "4 stops")))

```

##Impleenting model for goair
```{r}
# Example: Using lm() function for linear regression
model <- lm(Price ~ Duration + Total_Stops, data = output_tables_goair)
model

```
```{r}
# Assuming your data frame is named Data_Train
output_tables_indigo$Duration <- as.character(output_tables_indigo$Duration)

# Extract hours and minutes
hours <- as.numeric(substring(output_tables_indigo$Duration, 1, regexpr("h", output_tables_indigo$Duration) - 1))
minutes <- as.numeric(substring(output_tables_indigo$Duration, regexpr(" ", output_tables_indigo$Duration) + 1, nchar(output_tables_indigo$Duration) - 1))

# Calculate total duration in minutes
total_minutes <- hours * 60 + minutes

# Replace the original 'Duration' column with the new numeric column
output_tables_indigo$Duration <- total_minutes


output_tables_indigo <- na.omit(output_tables_indigo)



```

```{r}
# Example: Convert Total_Stops to numeric
output_tables_indigo$Total_Stops <- as.numeric(factor(output_tables_indigo$Total_Stops, levels = c("non-stop", "1 stop", "2 stops", "3 stops", "4 stops")))
```

##Implementing model for indigo

```{r}
# Example: Using lm() function for linear regression
model <- lm(Price ~ Duration + Total_Stops, data = output_tables_indigo)
model
```

```{r}
# Assuming your data frame is named Data_Train
output_tables_jetairways$Duration <- as.character(output_tables_jetairways$Duration)

# Extract hours and minutes
hours <- as.numeric(substring(output_tables_jetairways$Duration, 1, regexpr("h", output_tables_jetairways$Duration) - 1))
minutes <- as.numeric(substring(output_tables_jetairways$Duration, regexpr(" ", output_tables_jetairways$Duration) + 1, nchar(output_tables_jetairways$Duration) - 1))

# Calculate total duration in minutes
total_minutes <- hours * 60 + minutes

# Replace the original 'Duration' column with the new numeric column
output_tables_jetairways$Duration <- total_minutes


output_tables_jetairways <- na.omit(output_tables_jetairways)

```

```{r}
# Example: Convert Total_Stops to numeric
output_tables_jetairways$Total_Stops <- as.numeric(factor(output_tables_jetairways$Total_Stops, levels = c("non-stop", "1 stop", "2 stops", "3 stops", "4 stops")))
```

##Implementing model for jet airways
```{r}
# Example: Using lm() function for linear regression
model <- lm(Price ~ Duration + Total_Stops, data = output_tables_jetairways)
model
```
```{r}
# Assuming your data frame is named Data_Train
output_tables_jetairwaysbusiness$Duration <- as.character(output_tables_jetairwaysbusiness$Duration)

# Extract hours and minutes
hours <- as.numeric(substring(output_tables_jetairwaysbusiness$Duration, 1, regexpr("h", output_tables_jetairwaysbusiness$Duration) - 1))
minutes <- as.numeric(substring(output_tables_jetairwaysbusiness$Duration, regexpr(" ", output_tables_jetairwaysbusiness$Duration) + 1, nchar(output_tables_jetairwaysbusiness$Duration) - 1))

# Calculate total duration in minutes
total_minutes <- hours * 60 + minutes

# Replace the original 'Duration' column with the new numeric column
output_tables_jetairwaysbusiness$Duration <- total_minutes


output_tables_jetairwaysbusiness <- na.omit(output_tables_jetairwaysbusiness)

```

```{r}
# Example: Convert Total_Stops to numeric
output_tables_jetairwaysbusiness$Total_Stops <- as.numeric(factor(output_tables_jetairwaysbusiness$Total_Stops, levels = c("non-stop", "1 stop", "2 stops", "3 stops", "4 stops")))
```


##Implementing model for jetairways business
```{r}
# Example: Using lm() function for linear regression
model <- lm(Price ~ Duration + Total_Stops, data = output_tables_jetairwaysbusiness)
model
```


```{r}
# Assuming your data frame is named Data_Train
output_tables_multipleairways$Duration <- as.character(output_tables_multipleairways$Duration)

# Extract hours and minutes
hours <- as.numeric(substring(output_tables_multipleairways$Duration, 1, regexpr("h", output_tables_multipleairways$Duration) - 1))
minutes <- as.numeric(substring(output_tables_multipleairways$Duration, regexpr(" ", output_tables_multipleairways$Duration) + 1, nchar(output_tables_multipleairways$Duration) - 1))

# Calculate total duration in minutes
total_minutes <- hours * 60 + minutes

# Replace the original 'Duration' column with the new numeric column
output_tables_multipleairways$Duration <- total_minutes


output_tables_multipleairways <- na.omit(output_tables_multipleairways)


```

```{r}
# Example: Convert Total_Stops to numeric
output_tables_multipleairways$Total_Stops <- as.numeric(factor(output_tables_multipleairways$Total_Stops, levels = c("non-stop", "1 stop", "2 stops", "3 stops", "4 stops")))

```


#Implementing model for multiple carriers

```{r}
# Example: Using lm() function for linear regression
model <- lm(Price ~ Duration + Total_Stops, data = output_tables_multipleairways)
model
```
```{r}
# Assuming your data frame is named Data_Train
output_tables_multiplecarriers_premium$Duration <- as.character(output_tables_multiplecarriers_premium$Duration)

# Extract hours and minutes
hours <- as.numeric(substring(output_tables_multiplecarriers_premium$Duration, 1, regexpr("h", output_tables_multiplecarriers_premium$Duration) - 1))
minutes <- as.numeric(substring(output_tables_multiplecarriers_premium$Duration, regexpr(" ", output_tables_multiplecarriers_premium$Duration) + 1, nchar(output_tables_multiplecarriers_premium$Duration) - 1))

# Calculate total duration in minutes
total_minutes <- hours * 60 + minutes

# Replace the original 'Duration' column with the new numeric column
output_tables_multiplecarriers_premium$Duration <- total_minutes


output_tables_multiplecarriers_premium <- na.omit(output_tables_multiplecarriers_premium)


```

```{r}
output_tables_multiplecarriers_premium$Total_Stops <- as.numeric(factor(output_tables_multiplecarriers_premium$Total_Stops, levels = c("non-stop", "1 stop", "2 stops", "3 stops", "4 stops")))
```

##Implementing model for multiple carriers premium

```{r}
# Example: Using lm() function for linear regression
model <- lm(Price ~ Duration + Total_Stops, data = output_tables_multiplecarriers_premium)
model
```

```{r}
# Assuming your data frame is named Data_Train
output_tables_spicejet$Duration <- as.character(output_tables_spicejet$Duration)

# Extract hours and minutes
hours <- as.numeric(substring(output_tables_spicejet$Duration, 1, regexpr("h", output_tables_spicejet$Duration) - 1))
minutes <- as.numeric(substring(output_tables_spicejet$Duration, regexpr(" ", output_tables_spicejet$Duration) + 1, nchar(output_tables_spicejet$Duration) - 1))

# Calculate total duration in minutes
total_minutes <- hours * 60 + minutes

# Replace the original 'Duration' column with the new numeric column
output_tables_spicejet$Duration <- total_minutes


output_tables_spicejet <- na.omit(output_tables_spicejet)


```

```{r}
output_tables_spicejet$Total_Stops <- as.numeric(factor(output_tables_spicejet$Total_Stops, levels = c("non-stop", "1 stop", "2 stops", "3 stops", "4 stops")))
```

##Implementing model for sicejet

```{r}
model <- lm(Price ~ Duration + Total_Stops, data = output_tables_spicejet)
model
```
```{r}
# Assuming your data frame is named Data_Train
output_tables_vistara$Duration <- as.character(output_tables_vistara$Duration)

# Extract hours and minutes
hours <- as.numeric(substring(output_tables_vistara$Duration, 1, regexpr("h", output_tables_vistara$Duration) - 1))
minutes <- as.numeric(substring(output_tables_vistara$Duration, regexpr(" ", output_tables_vistara$Duration) + 1, nchar(output_tables_vistara$Duration) - 1))

# Calculate total duration in minutes
total_minutes <- hours * 60 + minutes

# Replace the original 'Duration' column with the new numeric column
output_tables_vistara$Duration <- total_minutes


output_tables_vistara <- na.omit(output_tables_vistara)



```


```{r}
output_tables_vistara$Total_Stops <- as.numeric(factor(output_tables_vistara$Total_Stops, levels = c("non-stop", "1 stop", "2 stops", "3 stops", "4 stops")))
```

##Implementing model for vistara

```{r}
model <- lm(Price ~ Duration + Total_Stops, data = output_tables_vistara)
model
```

